An Efficient Forecasting Approach\\ to Reduce Boundary Effects in Real-Time Time-Frequency Analysis

### 2021-02-01 Paper/BoundEffRed.tex
new XPs
paper v2

\begin{figure}
\centering
\includegraphics[width=.48\textwidth]{PPGsig.eps}
\caption{A segment of PPG signal (top) and the right boundary of a TF representation determined by the SST without extension (bottom left), and the right boundary of a TF representation determined by the SST with the proposed boundary effect reduction algorithm by forecasting (bottom right). The window length for the SST is 12~seconds. Videos of these real-time SSTs are available online at \url{https://github.com/AdMeynard/BoundaryEffectsReduction}}
\label{fig:ex.intro}
\end{figure}

@@

\section{Conclusion}
\label{se:conclusion}
In this paper, we propose an algorithm, named {\sf BoundEffRed}, for the real-time reduction of boundary effects in TF representations. This method is based on an extension of the signal obtained by a simple-minded and numerically efficient forecasting. We have shown theoretically that the chosen dynamic model is sufficient to extend signals formed by a sum of sine waves. Moreover, the low computational time allows us to switch to a real-time implementation of {\sf BoundEffRed}, unlike other existing forecasting methods. The numerical results also confirmed the robustness to noise of {\sf BoundEffRed}, as well as its ability to be applied to many TF representations. Additional applications to ECG and atrial blood pressure signals are included in the Supplementary Materials.

>>>>

\begin{figure}
\centering
\includegraphics[width=.48\textwidth]{PPGsig.eps}
\caption{A segment of PPG signal (top) and the right boundary of a TF representation determined by the SST without extension (bottom left), and the right boundary of a TF representation determined by the SST with the proposed boundary effect reduction algorithm by forecasting (bottom right). The window length for the SST is 12~seconds. {\color{red}Videos of these real-time SSTs are available online at \url{https://github.com/AdMeynard/BoundaryEffectsReduction}.}}
\label{fig:ex.intro}
\end{figure}

@@

\section{Conclusion}
\label{se:conclusion}
In this paper, we propose an algorithm, named {\sf BoundEffRed}, for the real-time reduction of boundary effects in TF representations. This method is based on an extension of the signal obtained by a simple-minded and numerically efficient forecasting. We have shown theoretically that the chosen dynamic model is sufficient to extend signals formed by a sum of sine waves. Moreover, the low computational time allows us to switch to a real-time implementation of {\sf BoundEffRed}, unlike other existing forecasting methods. The numerical results also confirmed the robustness to noise of {\sf BoundEffRed}, as well as its ability to be applied to many TF representations. Additional applications to ECG and PPG are included in the Supplementary Materials.

### 2021-02-01 Paper/results.tex
paper v2

\begin{figure}
\centering
\includegraphics[width=.48\textwidth]{Resp2.eps}
\caption{Two-component respiratory signal (top, yellow), and the associated {\sf SigExt} extension (blue); the simultaneously recorded ECG signal is below.}
\label{fig:resp.2}
\end{figure}

@@

\subsubsection{Photoplethysmogram}
\label{ssse:ppg}
We perform a study similar to the previous one on a $640$-second-long photoplethysmogram (PPG) signal extracted from the Physionet dataset~\cite{Pimentel17toward, Goldberger00physiobank}, sampled at $\fs=125$~Hz. A portion of this signal is displayed in Fig.~\ref{fig:ppg}. The estimated 5 seconds extensions of this segment obtained by {\sf SigExt}, EDMD, and GPR forecastings  are superimposed to the ground-truth extension in Fig.~\ref{fig:ppg}.

>>>>

\begin{figure}
\centering
\includegraphics[width=.48\textwidth]{Resp2.eps}
\caption{Two-component respiratory signal (top, yellow), and the associated {\sf SigExt} extension (blue); the simultaneously recorded ECG signal is below. The vertical magenta dotted lines indicate the cardiac cycles in the respiratory signal.}
\label{fig:resp.2}
\end{figure}

@@

\subsubsection{Photoplethysmogram}
\label{ssse:ppg}
We consider a $640$-second photoplethysmogram (PPG) signal extracted from the Physionet dataset~\cite{Pimentel17toward, Goldberger00physiobank}, sampled at $\fs=125$~Hz. A portion of this signal is displayed in Fig.~\ref{fig:ppg}. The estimated 5-second extensions of this segment obtained by {\sf SigExt}, EDMD, and GPR forecastings  are superimposed to the ground-truth extension in Fig.~\ref{fig:ppg}.
